Multiscale Modeling of the Paradoxical Roles of the Immune System in EMT-Mediated Cancer

### 2019-02-25 Paper/Paper.tex
Up to last par of intro

@@

Recent work on cancer-immune interactions has shown that the inflammatory conditions of the TME can play large and sometimes surprising roles in tumor growth.
Guo describes a model in which the inflammatory state of the TME affects the cell cycles of the stem cells by increasing proliferation, decreasing apoptosis, and enhancing DNA damage that leads to mutations\cite{guo2017multiscale}.
Guo uses the model to show that while inflammation does have an oncogenic effect, it can also have an onco-protective role as periods of mild inflammation are better at preventing cancer than periods of no inflammation in patients that have intermittent bouts of severe inflammation.
However, the aspect of the model that included the immune system was minimal: regardless of the inflammatory environment, any cells with sufficient pathway mutations (2 in their model) had a fixed probability of being cleared by the metabolism-immune balance response. 
In this paper, we hope to improve the model by including a more robust immune module and exploring how this axis will improve our understanding of inflammatory effects on the tumor.
In addition, we explore an extra component of Guo's stem cells: where they lie on the epithelial-mesenchymal axis.
So, in total, we will explore the joint interactions of the tumor, the immune system, and the epithelial-mesenchymal spectrum.
We will also study the effects of the TME on these interactions.

>>>>

Recent work on cancer-immune interactions has shown that the inflammatory conditions of the TME can play large and sometimes surprising roles in tumor growth.
For example, a mathematical model was developed to couple the inflammatory state of the TME with the cell cycles of the stem cells by increasing proliferation, decreasing apoptosis, and enhancing DNA damage that leads to mutations\cite{guo2017multiscale}.
The work shows that while inflammation does have an oncogenic effect, it can also have an onco-protective role as periods of mild inflammation are better at preventing cancer than periods of no inflammation in patients that have intermittent bouts of severe inflammation.
However, the aspect of the model that included the immune system is minimal and the connection with EMT is not included.
%However, the aspect of the model that included the immune system was minimal: regardless of the inflammatory environment, any cells with sufficient pathway mutations (2 in their model) had a fixed probability of being cleared by the metabolism-immune balance response. 
Here, we include a more robust immune module and explore how this immune module will improve our understanding of inflammatory effects on the tumor, and also include the epithelial-mesenchymal axis.
%In addition, we explore an extra component of Guo's stem cells: where they lie on the epithelial-mesenchymal axis.
Such additions will allow us to explore the interactions of the tumor, the immune system, and the epithelial-mesenchymal spectrum as well as the effects of the TME on these interactions.
%We will also study the effects of the TME on these interactions.

@@
